The Lipid Interactome

### 2025-02-25 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
minor updates to background sections

copyright:
  holder: "Gaelen Guzman"
  year: 2025
authors:
  - name: "Gaelen Guzman"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-7696-6034
    corresponding: true
    email: gaelen.guzman@lipidinteractome.org
  - name: "Carsten Schultz"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-5824-2171
  - name: "Fikadu Tafesse"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-8575-4164

@@

Gaelen Guzman^1,^*, Carsten Schulz^1^, Fikadu G. Tafesse^1^

^1^ = Oregon Health & Science University; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
:::

>>>>

copyright:
  holder: "Gaelen Guzman"
  year: 2025
authors:
  - name: "Gaelen Guzman"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-7696-6034
    corresponding: true
    email: gaelen.guzman@lipidinteractome.org
  - name: "Frank Stein"
    affiliations:
      - name: "European Molecular Biology Laboratory"
        city: Heidelberg
        country: Germany
        postal-code: 69117
    orcid: 0000-0001-9695-1692
  - name: "Carsten Schultz"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-5824-2171
  - name: "Fikadu Tafesse"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-8575-4164

@@

Gaelen Guzman^1,^*, Frank Stein^2^, Carsten Schulz^1^, Fikadu G. Tafesse^1^

^1^ = Oregon Health & Science University, Portland, OR, USA; ^2^ = European Molecular Biology Laboratory, Heidelberg, Germany * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
:::
